\chapter{Acknowledgments}
%\addcontentsline{toc}{chapter} {\protect\numberline{Acknowledgments\hspace{-96pt}}}

%The past few years have been some of the hardest of my live. Writing a P
Writing my thesis has been one of the hardest tasks in my life, and I couldn't have completed it without the support from my friends, family and the computing department. 

Firstly, I would like to thank my two supervisors, Laurent Mathy and Nicholas Race. They have kept me on the straight and narrow, always pointing me in the right direction. I would like to especially thank Laurent, for his tough supervision, which at times seemed harsh, but on reflection pushed me to become a far better researcher. I am also appreciative of Michael Fry's guidance, who in the last year has infused me with new ideas, and direction.

%I would like to thank my friends for  when I needed them, and sometimes when I didn't.
My friends have been there for me through my university life and constantly offering distractions from my studies, sometimes when I needed it, and others times when I didn't! Nevertheless, their backing has been greatly appreciated, especially my housemates, who have offered a good sounding board when I needed to work through a problem. A special thank you should go to Nicola, who in the last few weeks has greatly helped with proofreading of my thesis.

Finally, I would like to thank my parents and brother for being supportive during my PhD journey, and there for me when I needed them.

%, even if they have never quite understood what I've been doing.


%The Engineering and Physical Sciences Research Council (EPSRC) for funding

%\begin{itemize}
%    \item Academic People
%    \item Friends \& Family
%\end{itemize}

\singlespacing
\vspace*{1cm}
\begin{center}
    \it ``Time waits for no one'' \hspace*{0.5cm}
\end{center}
\begin{flushright}
    \small The Rolling Stones - 1974\hspace*{3cm}
\end{flushright}
\doublespacing

%"Time waits for no man" is originally a quote from a section by Death in the famous medieval play "Everyman" regarding certainty. The original line is in middle English is "For wete you well the tyde abydeth no man" but most schlars attribute this 'tyde' as a statement of time, as in Christmastide, etc. rather than a reference to the tides themselves. However, misunderstanding of the older form of language have led to the the common day phrase 'time and the tides wait for no man' which can be found in several literary allusions as well as movies such as Shakespeare in Love.
